### 2019-07-09 README.Rmd
Update other README.md
Fix some documentation references

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
submitted.

It has been permanently archived at Zenodo with the DOI shown above. The raw 
MS data has been deposited in the ProteomeXchange Consortium database via 
the PRIDE partner repository with the data set identifiers PXD014367, 
PXD014388, and PXD014389.

The compendium includes all the data, code, and text associated with the 
publication. It is structured as an R package to facilitate reproducilibity and 
distribution. The principles and motivations behind using research compendiums 
for academic research is detailed in 
[Marwick et al. (2018)](https://doi.org/10.1080/00031305.2017.1375986).

The R package [rrtools](https://github.com/benmarwick/rrtools) was used in the 
production of this compendium.

@@

@@

# install full compendium (functions, data, vignettes, manuscript) 
# and other packages required to build vignettes and manuscript
devtools::install_github("csdaw/candidaev", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         dependencies = TRUE)
```

@@

Three HTML vignettes detailing the analysis procedures used in the manuscript 
are included in this research compendium. These 
vignettes can be viewed with:

@@

#### Building the manuscript

>>>>

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. _Molecular and Cellular_ 
_Proteomics_, submitted.

It has been permanently archived at Zenodo with the DOI shown above. The raw 
MS data has been deposited in the ProteomeXchange Consortium database via 
the PRIDE partner repository with the data set identifiers PXD014367, 
PXD014388, and PXD014389. The analysis techniques and workflow used in this 
compendium were derived from the _Bioconductor_ package 
**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^.

The compendium includes all the data, code, and text associated with the 
publication. It is structured as an R package to facilitate reproducilibity and 
distribution. The principles and motivations behind using research compendiums 
for academic research is detailed in 
[Marwick et al. (2018)](https://doi.org/10.1080/00031305.2017.1375986). 
The R package **[rrtools](https://github.com/benmarwick/rrtools)**^2^ was used 
in the production of this compendium.

@@

### References

1. Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen, 
   M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS. 
   _Nature Protocols_, **13**, 530-550. 
   [doi:10.1038/nprot.2017.147](https://doi.org/10.1038/nprot.2017.147)

2. Marwick, B., Boettiger, C., Mullen, L. (2018). Packaging data analytical 
   work reproducibly using R (and friends). _The American Statistician_, 
   **72**(1), 80-88. 
   [doi:10.1080/00031305.2017.1375986](https://doi.org/10.1080/00031305.2017.1375986)

@@

# install full compendium (functions, data, vignettes, manuscript) 
# and other packages required to build vignettes and manuscript
devtools::install_github("csdaw/candidaev", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         dependencies = TRUE, build_vignettes = TRUE)
```

@@

Three HTML vignettes detailing the analysis procedures used in the manuscript 
are included in this research compendium. They are automatically built from 
scratch when the full research compendium is installed with `devtools`. These 
vignettes can be viewed with:

@@

#### Viewing the manuscript

The manuscript `.pdf` file, as submitted, can be downloaded 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

#### Building the manuscript from scratch
